Pottery decor as networks on the Middle Niger

### 2024-03-04 analysis/paper/paper.Rmd
without twisted

```{r community detection, hide = 'results', echo=FALSE}
# use louvain clustering method to assign clusters to nodes
decor_graph <- decor_graph |>
  activate(nodes) |>
  mutate(louvain = as.character(group_optimal()))

# calculate modularity of louvain clustering
modularity <- decor_graph |>
  activate(nodes) |>
  mutate(modularity = graph_modularity(group = as.factor(louvain))) |>
  pull(modularity) |>
  head(1)
```

@@

# igraph transformation loses the node attributes, so we put them back
early_flat_nodes <- early_flat |>
  activate(nodes) |>
  as_tibble()
early_flat_bb <- early_flat_bb |>
  activate(nodes) |>
  mutate(label = early_flat_nodes$label,
         lat = early_flat_nodes$lat, lon = early_flat_nodes$lon)

>>>>

```{r community detection, hide = 'results', echo=FALSE}
# use louvain clustering method to assign clusters to nodes
decor_graph <- decor_graph |>
  activate(edges) |> 
  filter(!name == "twisted_cord_roulette") |> 
  activate(nodes) |>
  mutate(louvain = as.character(group_optimal()))

# calculate modularity of louvain clustering
modularity <- decor_graph |>
  activate(nodes) |>
  mutate(modularity = graph_modularity(group = as.factor(louvain))) |>
  pull(modularity) |>
  head(1)

decor_graph

@@

# igraph transformation loses the node attributes, so we put them back
early_flat_nodes <- early_flat |>
  activate(nodes) |>
  as_tibble()
early_flat_bb <- early_flat_bb |>
  activate(nodes) |>
  mutate(label = early_flat_nodes$label,
         lat = early_flat_nodes$lat, 
         lon = early_flat_nodes$lon
         )
